---
title: "Untitled"
format: docx
editor: visual
---

```{r}
library(here)
library(tidyverse)
library(readr)

ggplot(data = se)+ geom_line(aes(x=year,y=visitors, color=state))+labs(y='visitation') +
  labs(x = "Year", y = "Visitors")+
  ggtitle("Visitation Trends in US South East National Parks between 1972-2016")
```

```{r}
library(here)
library(tidyverse)
library(readr)
ggplot(data = acadia) + 
  geom_point(aes(x = year, y = visitors)) +
  geom_line(aes(x = year, y = visitors)) +
  geom_smooth(aes(x = year, y = visitors)) +
  labs(title = "Acadia National Park Visitation between 1920 and 2020",
       y = "Visitation",
       x = "Year") +
  theme_bw()

```

## Note:

This week was a little stressful with personal matters, unfortunately, so I wasn't able to give this assignment my all in terms of using relevant data to my project. I found it helpful instead to go back and slowly go through the steps to learn how to make graphs using the National Park data. I understand if this means a lower grade- and I look forward to continue working on my ggplot skills! My lab research techs are hoping to send me relevant data this week and I am excited to play around with that in the coming weeks. Thank you!
